Accelerating Burn Speed of Birch Wood Popsicle Sticks

### 2022-05-01 paper/paper.Rmd
Add citations and footnotes

---
title: "Accelerating Burn Speed of Birch Wood Popsicle Sticks"
author: "E. Croffoot-Suede, S. Kim"
date: "May 2, 2022"
output:
  pdf_document:
    pandoc_args: --listings
    includes:
      before_body: title.sty
      in_header: preamble.tex
---

@@

In order to find which groups have a significant difference, we need to use an associated pairwise comparison procedure that can also be used against arbitrary incomplete block designs. To determine this, we created a novel pairwise multiple comparisons procedure that can be used on arbitrary incomplete block designs:

@@

However, we believe that the novel pairwise multiple comparisons procedure that we designed would still be valid given data obtained in an arbitrary incomplete block design. For example, suppose we were looking at data for a factory that produces products in batches, but which does not produce every batch every day. This would generate data in an arbitrary incomplete block design, where a metric of the product is the response, the batch is the treatment, and the day is the block. Using our procedure, we believe that we could diminish the block effect of days in the analysis and come up with an appropriate pairwise multiple comparison between the batches.

@@

>>>>

---
title: "Accelerating Burn Speed of Birch Wood Popsicle Sticks"
author: "E. Croffoot-Suede, S. Kim"
date: "May 2, 2022"
output:
  pdf_document:
    pandoc_args: --listings
    includes:
      before_body: title.sty
      in_header: preamble.tex
bibliography: citations.bib
csl: american-statistical-association.csl
nocite: '@*'
---

@@

In order to find which groups have a significant difference, we need to use an associated pairwise comparison procedure that can also be used against arbitrary incomplete block designs. To determine this, we used a novel pairwise multiple comparisons procedure that can be used on arbitrary incomplete block designs:^[This novel pairwise multiple comparisons procedure was created with the assistance of Dr. Erin Leatherman and Dr. Bradley Hartlaub, 2022.]

@@

However, we believe that the novel pairwise multiple comparisons procedure that we used would still be valid given data obtained in an arbitrary incomplete block design. For example, suppose we were looking at data for a factory that produces products in batches, but which does not produce every batch every day. This would generate data in an arbitrary incomplete block design, where a metric of the product is the response, the batch is the treatment, and the day is the block. Using our procedure, we believe that we could diminish the block effect of days in the analysis and come up with an appropriate pairwise multiple comparison between the batches.

@@

## References
